Single Site, Single Disturbance

### 2020-11-12 SingleSite_SingleDisturb.Rmd
SSSD: update todo with more detail about SIPNET test & need for real world SSSD-MultiPool: migrate code to work with VSEM

## Todo
-   Tweak model to have a simple C budget -- where does the C go when the model doesn't assimilate disturbance?
-   Apply to SIPNET SDA
-   Calibrate state and transition probabilities for a single region
-   Upgrade code to multinomial
-   Add PFT switching
-   Add ensemble weighting so that we can manage ensemble sizes
-   Add "fusion" if a case becomes too rare to worry about
-   Think about whether we need to add LULC state to state variables & how LULC state would be assimilated
-   Test against subseasonal dynamics (e.g. distinguishing phenology from disturbance)
-   investigate whether we need a "jumpback" capacity once disturbance event type and timing is resolved
-

>>>>

## Todo
-   Tweak model to have a simple C budget -- where does the C go when the model doesn't assimilate disturbance?
-   Calibrate state and transition probabilities for a single region
-   Upgrade code to multinomial
-   Add PFT switching
-   Apply to SIPNET SDA
    - version of code into PEcAn
    - test coupling to SIPNET
-   Real-world data examples
-   Add ensemble weighting so that we can manage ensemble sizes
-   Add "fusion" if a case becomes too rare to worry about
-   Think about whether we need to add LULC state to state variables & how LULC state would be assimilated
-   Test against subseasonal dynamics (e.g. distinguishing phenology from disturbance)
-   investigate whether we need a "jumpback" capacity once disturbance event type and timing is resolved
-
